Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-10 paper/paper.tex
Cardelli ref in bib

\begin{abstract}
  Reynolds' relational parametricity provides a powerful way to reason
  about programs in terms of invariance under changes of data
  representation. A dazzling array of applications of Reynolds' theory
  exists, exploiting invariance to yield ``free theorems'',
  uninhabitation results, and encodings of algebraic datatypes.
  Outside computer science, invariance is a common theme running
  through many areas of mathematics and physics. For example, the area of
  a triangle is unaltered by rotation or flipping. If we scale a
  triangle, then we scale its area, maintaining an invariant
  relationship between the two. The transformations under which
  properties are invariant are often organised into groups, with the
  algebraic structure reflecting the composability and invertibility
  of transformations.

@@

\bibitem{bernardy12proofs} 
J.-P.~Bernardy, P.~Jansson, R.~Paterson.
Proofs for free: Parametricity for dependent types.
{\em Journal of Functional Programming} 22(2), pp. 107-152, 2012.

@@

\bibitem{PittsAM:parpoe}
A.~M.~Pitts.  Parametric Polymorphism and Operational Equivalence.
{\em Mathematical Structures in Computer Science} 10(3), pp. 321-359,
2000.

\bibitem{reed10distance}
J.~Reed and B.~C.~Pierce.  Distance Makes the Types Grow Stronger.
Proceedings, International Conference on Functional Programming,
pp. 157-169, 2010.

>>>>

\begin{abstract}
  Reynolds' relational parametricity provides a powerful way to reason
  about programs in terms of invariance under changes of data
  representation. A dazzling array of applications of Reynolds' theory
  exists, exploiting invariance to yield ``free theorems'',
  uninhabitation results, and encodings of algebraic datatypes.
  Outside computer science, invariance is a common theme running
  through many areas mathematics and physics. For example, the area of
  a triangle is unaltered by rotation or flipping. If we scale a
  triangle, then we scale its area, maintaining an invariant
  relationship between the two. The transformations under which
  properties are invariant are often organised into groups, with the
  algebraic structure reflecting the composability and invertibility
  of transformations.

@@

\bibitem{bernardy12proofs} 
J.-P.~Bernardy, P.~Jansson, R.~Paterson.
Proofs for free: Parametricity for dependent types.
{\em Journal of Functional Programming} 22(02), pp. 107-152, 2012.

\bibitem{Cardelli}
L.~Cardelli, P.~Gardner.
Processes in Space.
{\em Programs, Proofs, Processes}: Proc, 6th Conference on Computability in Europe, pp 78-87, LNCS vol. 6158, 2010.

@@

\bibitem{PittsAM:parpoe}
A.~M.~Pitts.  Parametric Polymorphism and Operational Equivalence.
{\em Mathematical Structures in Computer Science} 10, pp. 321-359,
2000.

\bibitem{reed10distance}
J.~Reed and B.~C.~Pierce.  Distance Makes the Types Grow Stronger.
Proceeding, International Conference on Functional Programming,
pp. 157-169, 2010.
